\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2024-04-18 paper.tex

\section*{Data Availability}
The public GitHub repository at
\url{https://github.com/tskit-dev/what-is-an-arg-paper} can be
used to reproduce all figures and tables in this paper.
In particular this includes
the ARG used in Fig.~\ref{fig-ancestry-resolution} as well as
the simulation code and functions
used to generate Fig.~\ref{fig-inferred-args} and Fig.~\ref{fig-simplification}.
This includes the software versions, parameter settings, and
(where necessary) functions to convert
software outputs to the \texttt{tskit} gARG format.

>>>>

\section*{Data Availability}
All code used to generate figures and run analyses is available on GitHub at
\url{https://github.com/tskit-dev/what-is-an-arg-paper}.
